Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-04-22 awipev-CO2.Rmd
comment all TA parts except salinity relatinship

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour_copy.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  # dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
  #        AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
  #        #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
  #        #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
  #        ) %>%
  # variables passed through despike with "-filtered" have been renamed without sufix.
  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, temp_sf = T_seaF, ph_dur = ph_dur_filtered)
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))

@@

# Conversion of spectro pH to insitu mix T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet)& !is.na(sal_insitu_ctd) )
pH_seafet <- pH_seafet %>%
  dplyr::mutate(pH_s_seafet_temp_mix = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_mix, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_mix,Pt=0,Sit=0))

@@

# TA
# to create periods according to TA deployments

@@

at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT,at)
at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
   #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
  #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
  dySeries("AT", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
  dyAxis("y",valueRange = c(2000, 2650)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

f <- as.data.frame(table(d_all$at))
#sum(f$Freq)  
# Number of outliers removed in the dataset
# numberOutliers <- length(which((dat_ATnoNA$outliers > 0)))

@@

```{r First period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
#Interpolation of continuous sensor data to match a maximum of reference data.
TAinterp_all <-approx(d_all$datetime, d_all$AT, xout=d_all$datetime, method="linear", rule=2)
names(TAinterp_all) <- c("datetime", "AT_interp")
TAinterp_all <- as.data.frame(TAinterp_all)
d_all$AT_interp <- TAinterp_all$AT_interp

# create a column with difference between sensor and ref
d_all <- d_all%>%
  dplyr::mutate(diff_ta =  at-AT_interp )
# create colum with instrument number
d_all <- d_all %>%
  dplyr::mutate(TA_period= ifelse(datetime >= "2016-02-26 00:00:00" & datetime < "2017-02-09 12:00:00", "TA1",
                            ifelse(datetime >= "2017-02-09 12:00:00" & datetime < "2017-03-10 12:00:00", "TA2",
                            ifelse(datetime >= "2018-01-07 00:00:00" & datetime < "2018-06-20 00:00:00", "TA3",
                            ifelse(datetime >= "2018-07-31 00:00:00" & datetime < "2018-10-30 18:00:00", "TA4",
                            ifelse(datetime >= "2018-10-31 09:00:00" & datetime < "2019-01-16 09:00:00", "TA5",
                            ifelse(datetime >= "2019-01-26 13:25:00" , "TA6", "TA0")))))))

#remove outliers
calib_ta_first <- d_all%>%
  dplyr::select(datetime, closest_datetime,AT, AT_interp, at,diff_ta,TA_period)%>%
  dplyr::filter(TA_period =="TA1" & !is.na(at))
  #dplyr::filter( !is.na(at))#, diff_ta > -40 & diff_ta < 20 )
# & datetime != "2016-08-18 08:00:00" & datetime != "2016-12-29 12:00:00 ",!is.na(at))

# Parameters of regression
fit <- lm( data=calib_ta_first%>%filter(diff_ta <= 50), diff_ta ~ datetime)
at_slope_TA1 <- round(fit$coefficients[[2]] , digits=6)
at_slope1 <- round(at_slope_TA1 * 3600 *24 * 365.24, digits=2)
at_intercept1 <- round(fit$coefficients[[1]], digits= 2)
```

The slope is: `r #at_slope_TA1` x 3600 x 24 x 365.24 = `r #at_slope1` µmoles.kg-1.yr-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. Outliers are in red.

```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
 # Plot of regression
 p <- ggplot(calib_ta_first%>%filter(diff_ta <= 50),aes(datetime,diff_ta)) +
     geom_point() + geom_smooth(method='lm', se=FALSE)+
     geom_point(data= calib_ta_first%>%filter(diff_ta >= 50), aes(x=datetime, y=diff_ta), color="red")  +
   geom_hline(yintercept = 0, linetype="dashed" )+
   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                      "Intercept =",signif(fit$coef[[1]],5 ),
                      "Slope =",signif(fit$coef[[2]], 5),
                      "P =",signif(summary(fit)$coef[2,4], 5))) +
   ylab("Difference: Reference - Analyser") + xlab("Time") + scale_x_datetime(date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
 print(p)
 ggsave(paste0("figures/Diff_ref_TA_first_period.png"), p, units="cm")
```

##### **Third period**

```{r Third period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold',fig.align="center"}

 #remove outliers and remove period without TA measurements
 calib_ta_third <- d_all%>%
   dplyr::select(datetime, closest_datetime,AT, AT_interp, at,diff_ta, TA_period)%>%
   dplyr::filter(TA_period == "TA3" & !is.na(at))

 # Parameters of regression
 fit <- lm( data=calib_ta_third, diff_ta ~ datetime)
 at_slope_TA3 <- round(fit$coefficients[[2]] , digits=8)
 at_slope3 <- round(at_slope_TA3 * 3600 *24 * 365.24, digits=2)
 at_intercept3 <- round(fit$coefficients[[1]], digits= 2) # pas besoin ici.
```

The slope is in days: `r #at_slope_TA3` x 3600 x 24 x 365.24 = `r #at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers.

```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# # Plot of regression
 p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+
     geom_point() + geom_smooth(method='lm', se=FALSE)+
     #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
    geom_hline(yintercept = 0, linetype="dashed" )+
   geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
   #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                      "Intercept =",signif(fit$coef[[1]],5 ),
                      " Slope =",signif(fit$coef[[2]], 5),
                      " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") +
   scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
 print(p)
 ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm")
```

##### **Second period**

```{r Second period, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}

#remove outliers and remove period without TA measurements
calib_ta_second <- d_all%>%
  dplyr::select(datetime, closest_datetime, AT, AT_interp, at, diff_ta, TA_period)%>%
  dplyr::filter(TA_period == "TA2" & !is.na(at))

mean_offset <- mean(calib_ta_second$diff_ta)

For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r #mean_offset` µmoles.kg~-1~) was added to TA value as an offset.

#### **Final TA corrected data (Regression)**

The following plot shows the corrected TA data with regressions (Periods 1 and 3) and with offset (Period 2) applied according to Steffen's proposition.
It is clear that these corrected data (in green) cannot be used for periods 1 to 3. The jury is still out for period 4. The issue of salinity must be clarified before an assessment can be made.

```{r Correction applied, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}
# Correction for the 3 periods is apply
d_all <- d_all%>%
  dplyr::mutate(datetime_reg = as.numeric(datetime),
                at_intercept = ifelse(TA_period == "TA1", at_intercept1,
                               ifelse(TA_period == "TA3", at_intercept3, NA)),
                at_slope = ifelse(TA_period == "TA1", at_slope_TA1,
                           ifelse(TA_period == "TA3", at_slope_TA3, NA))
                )

d_all <- d_all%>%
 dplyr::mutate(TA_reg_corrected = ifelse(TA_period == "TA1", (AT + (d_all$datetime_reg * d_all$at_slope + at_intercept)),
                                        ifelse(TA_period == "TA2", (AT + mean_offset),
                                        ifelse(TA_period == "TA3", (AT + (datetime_reg * at_slope)+ at_intercept), NA))))

>>>>

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  # dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
  #        AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
  #        #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
  #        #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
  #        ) %>%
  # variables passed through despike with "-filtered" have been renamed without sufix.
  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, temp_sf = T_seaF)
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))

@@

# Conversion of spectro pH to insitu mix T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet) & !is.na(sal_insitu_ctd) & !is.na(temp_mix) )
pH_seafet <- pH_seafet %>%
  dplyr::mutate(pH_s_seafet_temp_mix = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_mix, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_mix,Pt=0,Sit=0))

@@

# # TA
# # to create periods according to TA deployments

@@

# at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT,at)
# at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
# dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
#    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
#   #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
#   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
#   dySeries("AT", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
#   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
#   dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
#   dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
#   dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
#   dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
#   dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
#   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
#   dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
#   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
#   dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
#   dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
#   dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
#   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
#   dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
#   dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
#   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
#   dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
#   dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
#   dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
#   dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
#   dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
#   dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
#   dyAxis("y",valueRange = c(2000, 2650)) %>%
#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
#   dyOptions( strokeWidth= 0) %>%
#   dyLegend(show = "follow")   %>%
#   dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
#     dyRangeSelector(height = 30, dateWindow= NULL) 
#  
f <- as.data.frame(table(d_all$at))
#sum(f$Freq)  
# Number of outliers removed in the dataset
# numberOutliers <- length(which((dat_ATnoNA$outliers > 0)))

@@

```{r First period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# #Interpolation of continuous sensor data to match a maximum of reference data.
# TAinterp_all <-approx(d_all$datetime, d_all$AT, xout=d_all$datetime, method="linear", rule=2)
# names(TAinterp_all) <- c("datetime", "AT_interp")
# TAinterp_all <- as.data.frame(TAinterp_all)
# d_all$AT_interp <- TAinterp_all$AT_interp
# 
# # create a column with difference between sensor and ref
# d_all <- d_all%>%
#   dplyr::mutate(diff_ta =  at-AT_interp )
# # create colum with instrument number
# d_all <- d_all %>%
#   dplyr::mutate(TA_period= ifelse(datetime >= "2016-02-26 00:00:00" & datetime < "2017-02-09 12:00:00", "TA1",
#                             ifelse(datetime >= "2017-02-09 12:00:00" & datetime < "2017-03-10 12:00:00", "TA2",
#                             ifelse(datetime >= "2018-01-07 00:00:00" & datetime < "2018-06-20 00:00:00", "TA3",
#                             ifelse(datetime >= "2018-07-31 00:00:00" & datetime < "2018-10-30 18:00:00", "TA4",
#                             ifelse(datetime >= "2018-10-31 09:00:00" & datetime < "2019-01-16 09:00:00", "TA5",
#                             ifelse(datetime >= "2019-01-26 13:25:00" , "TA6", "TA0")))))))
# 
# #remove outliers
# calib_ta_first <- d_all%>%
#   dplyr::select(datetime, closest_datetime,AT, AT_interp, at,diff_ta,TA_period)%>%
#   dplyr::filter(TA_period =="TA1" & !is.na(at))
#   #dplyr::filter( !is.na(at))#, diff_ta > -40 & diff_ta < 20 )
# # & datetime != "2016-08-18 08:00:00" & datetime != "2016-12-29 12:00:00 ",!is.na(at))
# 
# # Parameters of regression
# fit <- lm( data=calib_ta_first%>%filter(diff_ta <= 50), diff_ta ~ datetime)
# at_slope_TA1 <- round(fit$coefficients[[2]] , digits=6)
# at_slope1 <- round(at_slope_TA1 * 3600 *24 * 365.24, digits=2)
# at_intercept1 <- round(fit$coefficients[[1]], digits= 2)
```

<!-- The slope is: `r #at_slope_TA1` x 3600 x 24 x 365.24 = `r #at_slope1` µmoles.kg-1.yr-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. Outliers are in red. -->

<!-- ```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"} -->
<!--  # Plot of regression -->
<!--  p <- ggplot(calib_ta_first%>%filter(diff_ta <= 50),aes(datetime,diff_ta)) + -->
<!--      geom_point() + geom_smooth(method='lm', se=FALSE)+ -->
<!--      geom_point(data= calib_ta_first%>%filter(diff_ta >= 50), aes(x=datetime, y=diff_ta), color="red")  + -->
<!--    geom_hline(yintercept = 0, linetype="dashed" )+ -->
<!--    labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5), -->
<!--                       "Intercept =",signif(fit$coef[[1]],5 ), -->
<!--                       "Slope =",signif(fit$coef[[2]], 5), -->
<!--                       "P =",signif(summary(fit)$coef[2,4], 5))) + -->
<!--    ylab("Difference: Reference - Analyser") + xlab("Time") + scale_x_datetime(date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC") -->
<!--  print(p) -->
<!--  ggsave(paste0("figures/Diff_ref_TA_first_period.png"), p, units="cm") -->
<!-- ``` -->

<!-- ##### **Third period** -->

<!-- ```{r Third period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold',fig.align="center"} -->

<!--  #remove outliers and remove period without TA measurements -->
<!--  calib_ta_third <- d_all%>% -->
<!--    dplyr::select(datetime, closest_datetime,AT, AT_interp, at,diff_ta, TA_period)%>% -->
<!--    dplyr::filter(TA_period == "TA3" & !is.na(at)) -->

<!--  # Parameters of regression -->
<!--  fit <- lm( data=calib_ta_third, diff_ta ~ datetime) -->
<!--  at_slope_TA3 <- round(fit$coefficients[[2]] , digits=8) -->
<!--  at_slope3 <- round(at_slope_TA3 * 3600 *24 * 365.24, digits=2) -->
<!--  at_intercept3 <- round(fit$coefficients[[1]], digits= 2) # pas besoin ici. -->
<!-- ``` -->

<!-- The slope is in days: `r #at_slope_TA3` x 3600 x 24 x 365.24 = `r #at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers. -->

<!-- ```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"} -->
<!-- # # Plot of regression -->
<!--  p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ -->
<!--      geom_point() + geom_smooth(method='lm', se=FALSE)+ -->
<!--      #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  + -->
<!--     geom_hline(yintercept = 0, linetype="dashed" )+ -->
<!--    geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") + -->
<!--    #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+ -->
<!--    labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5), -->
<!--                       "Intercept =",signif(fit$coef[[1]],5 ), -->
<!--                       " Slope =",signif(fit$coef[[2]], 5), -->
<!--                       " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + -->
<!--    scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC") -->
<!--  print(p) -->
<!--  ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm") -->
<!-- ``` -->

<!-- ##### **Second period** -->

<!-- ```{r Second period, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'} -->

<!-- #remove outliers and remove period without TA measurements -->
<!-- calib_ta_second <- d_all%>% -->
<!--   dplyr::select(datetime, closest_datetime, AT, AT_interp, at, diff_ta, TA_period)%>% -->
<!--   dplyr::filter(TA_period == "TA2" & !is.na(at)) -->

<!-- mean_offset <- mean(calib_ta_second$diff_ta) -->

<!-- For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r #mean_offset` µmoles.kg~-1~) was added to TA value as an offset. -->

<!-- #### **Final TA corrected data (Regression)** -->

<!-- The following plot shows the corrected TA data with regressions (Periods 1 and 3) and with offset (Period 2) applied according to Steffen's proposition. -->
<!-- It is clear that these corrected data (in green) cannot be used for periods 1 to 3. The jury is still out for period 4. The issue of salinity must be clarified before an assessment can be made.  -->

<!-- ```{r Correction applied, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'} -->
<!-- # Correction for the 3 periods is apply -->
<!-- d_all <- d_all%>% -->
<!--   dplyr::mutate(datetime_reg = as.numeric(datetime), -->
<!--                 at_intercept = ifelse(TA_period == "TA1", at_intercept1, -->
<!--                                ifelse(TA_period == "TA3", at_intercept3, NA)), -->
<!--                 at_slope = ifelse(TA_period == "TA1", at_slope_TA1, -->
<!--                            ifelse(TA_period == "TA3", at_slope_TA3, NA)) -->
<!--                 ) -->

<!-- d_all <- d_all%>% -->
<!--  dplyr::mutate(TA_reg_corrected = ifelse(TA_period == "TA1", (AT + (d_all$datetime_reg * d_all$at_slope + at_intercept)), -->
<!--                                         ifelse(TA_period == "TA2", (AT + mean_offset), -->
<!--                                         ifelse(TA_period == "TA3", (AT + (datetime_reg * at_slope)+ at_intercept), NA)))) -->

<!-- at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT,at,TA_reg_corrected) -->
<!-- at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime) -->
<!-- dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>% -->
<!--    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>% -->
<!--   dySeries("AT", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>% -->
<!--   dySeries("TA_reg_corrected", label= "Corrected TA", color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>% -->
<!--   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% -->
<!--   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>% -->
<!--   dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>% -->
<!--   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>% -->
<!--   dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>% -->
<!--   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
<!--   dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>% -->
<!--   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>% -->
<!--   dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>% -->
<!--   dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>% -->
<!--   dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>% -->
<!--   dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>% -->
<!--   dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>% -->
<!--   dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>% -->
<!--   dyAxis("y",valueRange = c(1600, 2650)) %>% -->
<!--   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>% -->
<!--   dyOptions( strokeWidth= 0) %>% -->
<!--   dyLegend(show = "follow")   %>% -->
<!--   dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>% -->
<!--     dyRangeSelector(height = 30, dateWindow= NULL) -->
